---
title: "Nachiket Nareshkumar Pasrija (000918216)"
subtitle: "Predictive Data Analytics (DATA-420-A)"
output:
  html_document:
    df_print: paged
---
<style>
body {
text-align: justify}
</style>

### __Assignement 6__

```{r,message=FALSE}
library(tidyverse)
library(forecast)
library(tidyr)
```
<br>

#### __1. Load the dataset into a data frame__
```{r,message=FALSE}
data <- read.csv("~/retail_data.csv", header = TRUE)
```
<br>

#### __2. Create a decomposition plot.__
```{r,message=FALSE}
# Convert the data to a time series object
time_sereies_data <- ts(data$Sales, start = c(2018, 1), end = c(2023, 12), frequency = 12)

# Decompose the time series and create a plot
decomposed <- decompose(time_sereies_data)
plot(decomposed)
```  

In R, the standard practice for time series decomposition involves applying an additive model. This technique entails the partitioning of a time series into its original form and three fundamental components: the trend, the seasonal pattern, and remainder (or random/error).

<br>

#### __3. Train the model using ARIMA dataset.__
```{r,message=FALSE}
ARIMA <- auto.arima(time_sereies_data)
summary(ARIMA)
```

<br>

#### __4. Forecast the sales for the next 4, 8, and 12 months.__
```{r,message=FALSE}
forecast_4_months <- forecast(ARIMA, h = 4)
print(forecast_4_months)

forecast_8_months <- forecast(ARIMA, h = 8)
print(forecast_8_months)

forecast_12_months <- forecast(ARIMA, h = 12)
print(forecast_12_months)
```

